Data preparation B

### 2020-01-15 script/data-prep-B.Rmd

### Save 09 data

```{r}
save(dat09,file = "input/data/processed/dat09.RData")
```

@@

### Save 19 data
```{r}
save(dat19,file = "input/data/processed/dat19.RData")
```

>>>>

### Save 09 data
```{r}
save(dat09,file = "input/data/processed/dat09.RData")
```

@@

### Save 19 data
```{r}

save(dat19,file = "input/data/processed/dat19.RData")
```

### Save all years data
```{r}
dat99$year <- 1999
dat09$year <- 2009
dat19$year <- 2019
clw3<- bind_rows(dat99,dat09)
clw3<- bind_rows(clw3,dat19)
save(clw3,file = "input/data/processed/clw3.Rdata")
```
